Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-15 Revise-version.tex
txs auto checkin

>>>>

\begin{itemize}
	% Core denoising variables
	\item $\mathbf{x} \in \mathbb{R}^{B \times 2 \times 32 \times 32}$: Input CSI tensor where:
	\begin{itemize}
		\item $B$: Batch size
		\item $2$: Real and imaginary components
		\item $32 \times 32$: Delay and angular dimensions
	\end{itemize}

	\item $\tilde{\mathbf{x}} = \mathbf{x} + \mathbf{n}$: Noisy observation where $\mathbf{n} \sim \mathcal{N}(0,\sigma_n^2\mathbf{I})$

	\item $\sigma_n^2 = P \cdot 10^{-\text{SNR}_{\text{dB}}/10}$: Noise variance with:
	\begin{itemize}
		\item $P = \mathbb{E}[\|\mathbf{x}\|_2^2]$: Signal power
		\item $\text{SNR}_{\text{dB}}$: Signal-to-noise ratio in decibels
	\end{itemize}

	% RefineNet parameters
	\item Denoising operator $\mathcal{D}(\cdot)$ (RefineNet) implements:
	\begin{itemize}
		\item Parallel convolutional paths with kernel sizes $1\times7$ and $1\times5$
		\item LeakyReLU activation ($\alpha=0.3$)
		\item Residual learning: $\mathcal{D}(\tilde{\mathbf{x}}) = \tilde{\mathbf{x}} + \Delta(\tilde{\mathbf{x}})$
	\end{itemize}

	% Metrics
	\item Normalized MSE:
	\begin{equation}
		\text{NMSE} = \frac{\|\mathcal{D}(\tilde{\mathbf{x}}) - \mathbf{x}\|_F^2}{\|\mathbf{x}\|_F^2}
	\end{equation}
\end{itemize}

\begin{table}[ht]
	\centering
	\caption{Noise Resilience Hyperparameters}
	\label{tab:noise_params}
	\begin{tabular}{lc}
		\toprule
		Parameter & Value \\
		\midrule
		LeakyReLU slope ($\alpha$) & 0.3 \\
		BatchNorm momentum & 0.99 \\
		Training SNR range & $-5$ to $40$ dB \\
		Kernel sizes & $[1\times3]$, $[1\times5]$, $[1\times7]$ \\
		\bottomrule
	\end{tabular}
\end{table}
